doupi3

### 2023-01-31 outputs/paper.qmd
draft

```{r}
#| echo: false
#| message: false
#| warning: false
#homicide(NA), shooting(NA), motor theft
selected_crime_rate2021 <- cleaned_data |>
  select(population2021, homicide_rate2021, shootings_rate2021, theftfrom_motor_vehicle_rate2021)

homicide <-
  selected_crime_rate2021 |>
  ggplot(mapping = aes(x = population2021, y= homicide_rate2021))+
  geom_jitter() +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  labs(
    x = "Population",
    y = "Homocide Rate",
    title = "Relationship between population and homicide rate"
    )

shootings <-
  selected_crime_rate2021 |>
  ggplot(mapping = aes(x = population2021, y= shootings_rate2021))+
  geom_jitter() +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  labs(
    x = "Population",
    y = "Shootings Rate",
    title = "Relationship between population and shootings rate"
    )

motor <-
  selected_crime_rate2021 |>
  ggplot(mapping = aes(x = population2021, y= theftfrom_motor_vehicle_rate2021))+
  geom_jitter() +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  labs(
    x = "Population",
    y = "Motor theft Rate",
    title = "Relationship between population and motor theft rate"
    )

homicide /
  shootings /
  motor

```{r}
#| include: false
#| echo: false
#| message: false
#| warning: false
mean_crime_rate_each_year <- cleaned_data |>
  select(-population2021,-neighbothood_size) |>
  summarise_all(mean, na.rm = TRUE)

@@

# Reference

>>>>

```
```{r}
#| echo: false
#| message: false
#| warning: false
#| n-col: 2
#homicide(NA), shooting(NA), motor theft
selected_crime_rate2021 <- cleaned_data |>
  select(population2021, homicide_rate2021, shootings_rate2021, theftfrom_motor_vehicle_rate2021)

homicide <-
  selected_crime_rate2021 |>
  ggplot(mapping = aes(x = population2021, y= homicide_rate2021))+
  geom_jitter() +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  labs(
    x = "Population",
    y = "Homocide Rate",
    )

shootings <-
  selected_crime_rate2021 |>
  ggplot(mapping = aes(x = population2021, y= shootings_rate2021))+
  geom_jitter() +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  labs(
    x = "Population",
    y = "Shootings Rate",
    )

motor <-
  selected_crime_rate2021 |>
  ggplot(mapping = aes(x = population2021, y= theftfrom_motor_vehicle_rate2021))+
  geom_jitter() +
  geom_smooth(method = lm, se = FALSE) +
  theme_minimal() +
  labs(
    x = "Population",
    y = "Motor theft Rate",
    )

(homicide + shootings) /
  motor

```
```{r}
#| include: false
#| echo: false
#| message: false
#| warning: false
mean_crime_rate_each_year <- cleaned_data |>
  select(-population2021,-neighbothood_size) |>
  summarise_all(mean, na.rm = TRUE)

@@

```
```
